---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis-CI Build Status](http://badges.herokuapp.com/travis/mdsumner/nchelper?branch=master&env=BUILD_NAME=trusty_release&label=linux)](https://travis-ci.org/mdsumner/nchelper)
[![Build Status](http://badges.herokuapp.com/travis/mdsumner/nchelper?branch=master&env=BUILD_NAME=osx_release&label=osx)](https://travis-ci.org/mdsumner/nchelper) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/nchelper?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/nchelper) 


# nchelper

The goal of nchelper is to provide NetCDF variables as R arrays. 

## Installation

You can install nchelper from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/nchelper")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


 Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
