---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis-CI Build Status](http://badges.herokuapp.com/travis/mdsumner/nchelper?branch=master&env=BUILD_NAME=trusty_release&label=linux)](https://travis-ci.org/mdsumner/nchelper)
[![Build Status](http://badges.herokuapp.com/travis/mdsumner/nchelper?branch=master&env=BUILD_NAME=osx_release&label=osx)](https://travis-ci.org/mdsumner/nchelper) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/nchelper?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/nchelper) 


# nchelper

The goal of nchelper is to provide NetCDF variables as R arrays. 

## Installation

You can install nchelper from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/nchelper")
```

## Example

This is an example that reads an inbuilt data set of sea surface temperature. 

First, find the file and open the variable "sst" as object `a`. 

```{r example}
library(nchelper)
f <- system.file("extdata", "avhrr-only-v2.20180126.nc", package = "nchelper")
a <- nchelper(f, "sst")
dim(a)
names(a)
```

Now use standard indexing idioms to extract data from this 4D array. 

```{r four-d}
grcol <- grey(seq(0, 1, length.out = 12))
image(a[,,,], col = grcol)
image(a[400:800, 100:300,,], col = grcol)
plot(a[,360,,] * 0.01, ylim = c(20, 32), type = "l")
```



(Even though we asked for the variable "sst", we could have left it empty for a reminder about any available names.)

```{r variables}
a <- nchelper(f)
a[]
names(a)

## so we go for one of the 2D ones (sst, anom, err, ice)
err <- nchelper(f, "err")
image(err[,,,])
```


This is a cheap and easy way to investigate the contents of a source. 
```{r}
image(nchelper(f, "anom")[,,,], col = hcl(240, c = 25, l = 10:90))
```
 Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
